---
title: "Your Title Here"
author: 
  - name: "Your Name Here"
    email: "Your Email Here"
    affiliation: "Your University/Institution Here"
date: '`r format(Sys.time(), "%d/%m/%Y")`'
output: 
  html_document:
    theme: united
    highlight: pygments
    fig_caption: yes
    code_folding: hide
    df_print: kable
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
---

---

### Workshop introduction
In this document, we will load interview data and visualize it to gain insights into the data. We will also perform basic statistical tests to generate solid conclusions about the data.

The data can be found on: https://github.com/mtrauernicht/RStudio_workshop

## Data information



---

## Setup {.tabset}

<!-- little HTML script to do indentation of the table of contents -->
<script>
    $(document).ready(function() {
      $items = $('div#TOC li');
      $items.each(function(idx) {
        num_ul = $(this).parentsUntil('#TOC').length;
        $(this).css({'text-indent': num_ul * 10, 'padding-left': 0});
      });

    });
</script>

```{css, echo = FALSE}
div.sourceCode {
  overflow-x: hidden;
}
```

### Libraries
```{r setup, out.width= "80%", fig.align= "center", echo=FALSE, warning= FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
StartTime <-Sys.time()

# 8-digit Date tag:
Date <- substr(gsub("-","",Sys.time()),1,8) 
# libraries:
library(ggvisuals)

```

### Custom functions

```{r, out.width= "80%", fig.align= "center", echo=FALSE, warning= FALSE, message=FALSE}
SetFileName <- function(filename, initials) {
  # Set filename with extension and initials to make filename with date integrated.
  filename <- substitute(filename)
  initials <- substitute(initials)
  filename <- paste0(initials, Date, filename)
  filename
}

theme_classic_lines <- function() {
  theme_pubr(border = T, base_family = "Arial", legend = "top") +
            theme(panel.grid.major = element_line(colour = "#adb5bd", size = 0.1),
                  strip.background = element_rect(fill = "#ced4da")
            )
}

theme_classic_lines_45 <- function() {
  theme_pubr(border = T, base_family = "Arial", legend = "top", x.text.angle = 45) +
            theme(panel.grid.major = element_line(colour = "#adb5bd", size = 0.1),
                  strip.background = element_rect(fill = "#ced4da")
            )
}

theme_classic_lines_90 <- function() {
  theme_pubr(border = T, base_family = "Arial", legend = "top", x.text.angle = 90) +
            theme(panel.grid.major = element_line(colour = "#adb5bd", size = 0.1),
                  strip.background = element_rect(fill = "#ced4da")
            )
}

theme_set(theme_classic_lines())
```


### Load data

```{r}
# Here I load this: 



```

---

## Visualisation

```{r, out.width= "80%", fig.align= "center", echo=FALSE, warning= FALSE, message=FALSE}



```

---

## Results
```{r, out.width= "80%", fig.align= "center", echo=FALSE, warning= FALSE, message=FALSE}
```


### Exporting potential data
```{r, out.width= "80%", fig.align= "center", echo=FALSE, warning= FALSE, message=FALSE}
```


# Session Info
```{r}
paste("Run time: ",format(Sys.time()-StartTime))
getwd()
date()
sessionInfo()
```

